---
title: "ngsgenotype_snp"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Detect, load and clean files and genotypes:
```{r}
# Load libraries:
library(tidyverse)
library(ShortRead)
library(wesanderson)
source("genotyping_functions.r")

# Load all samples and mark controls and duplicates: # some negatives and positives are summarized if they are named the same(?)
allGenotypes <- ParseGenotypes(genotypePath = "../3_Genotyped_SNPs/")

# Remove duplicates and controls:
allGenotypes <- allGenotypes[allGenotypes$Status != "Duplicated", ] # no duplicated names are allowed past this point
allGenotypes <- allGenotypes[allGenotypes$Status != "Control", ] # no controls are allowed past this point

# Separate autosomal genotypes and sexual genotypes if there are no repeated names:
if(!any(duplicated(allGenotypes$Sample))) {
  sexString <- "X-*|Y-*"
  autoGenotypes <- allGenotypes[, !grepl(sexString, colnames(allGenotypes))]
  saveRDS(autoGenotypes, file = "autoGenotypes.rds")
  sexGenotypes <- cbind(Sample = allGenotypes$Sample, allGenotypes[, grepl(sexString, colnames(allGenotypes))])
  saveRDS(sexGenotypes, file = "sexGenotypes.rds")
} else {
  cat("Error: allGenotypes contains repeated sample names.")
}
```

# Filter/QC samples and loci:
```{r}
# Mark samples based on quality:
QCGenotypes <- QCMarking(autoGenotypes, minPresent = 75, targetStatus = c("Loaded"), newStatus = "High Quality") %>%
  QCMarking(minPresent = 67, maxPresent = 74, targetStatus = c("Loaded"), newStatus = "Medium Quality") %>%
  QCMarking(minPresent = 24, maxPresent = 66, targetStatus = c("Loaded"), newStatus = "Low Quality") %>%
  QCMarking(minPresent = 00, maxPresent = 23, targetStatus = c("Loaded"), newStatus = "Fail Quality") # perhaps use a more comprehensive function and collapse this into one line

# Quick overview of quality of samples:
table(QCGenotypes$Status)
```

# Cluster all working samples (>= 67 working loci) and identify samples/clusters to be removed:
```{r}
library(allelematch)

# Make new object:
processedGenotypes <- QCGenotypes

# Cluster all samples with sufficient quality:
loadedDataAll <- LoadAMData(processedGenotypes, targetStatus = c("Medium Quality", "High Quality")) # Load all samples with 67 or more working loci

{png(file="Outputs/amUniqueProfile_plot_All.png", width = 689, height = 425)
amProfileAll <- allelematch::amUniqueProfile(amDatasetFocal = loadedDataAll$Data, multilocusMap = loadedDataAll$AlleleKey, doPlot = TRUE, alleleMismatch = c(0:45))
dev.off()
saveRDS(amProfileAll, file = "amProfileAll.rds")
mmCutoff <- amProfileAll$alleleMismatch[amProfileAll$guessOptimum]}

uniqueBearsAll <- allelematch::amUnique(loadedDataAll$Data, multilocusMap = loadedDataAll$AlleleKey, alleleMismatch = mmCutoff)
allelematch::summary.amUnique(object = uniqueBearsAll, html = paste0("unique_bears_all_", mmCutoff, "_v1.html"))
allelematch::summary.amUnique(object = uniqueBearsAll, csv = paste0("unique_bears_all_", mmCutoff, "_v1.csv"))

# get clusters and high quality individuals:
clustersAll <- lapply(uniqueBearsAll$pairwise, function(x) {x$match$index})
samples75 <- processedGenotypes$Sample[processedGenotypes$Status == "High Quality"] # should this be placed after marking unclassified/multiplematched? To avoid to not keep orphans by mistake?

# check each one and see if they contain any matched sample from '75' run, note all samples in any who doesn't
GetOrphans <- function(hiqSamples, allClusters) {
  rmSamples <- c()
  for(curCluster in allClusters) {
    if(!any(curCluster %in% hiqSamples)) {
      rmSamples <- c(rmSamples, curCluster)
    }
  }
  return(unique(c(rmSamples, "0_EMPTY_NAME"))) # return orphaned samples
}

# Mark unclassified and multiplematched samples from all run:
processedGenotypes$Status[processedGenotypes$Sample %in% uniqueBearsAll$unclassified$index] <- "Unclassified"
processedGenotypes$Status[processedGenotypes$Sample %in% uniqueBearsAll$multipleMatches$index] <- "MultipleMatched"

# Get orphaned samples and mark them:
print(length(GetOrphans(hiqSamples = samples75, allClusters = clustersAll))) # number of newly added samples to be removed
processedGenotypes$Status[processedGenotypes$Sample %in% GetOrphans(samples75, clustersAll)] <- "Orphan"
```

# Recluster without samples chosen to be removed:
```{r}
# Make new object:
finalGenotypes <- processedGenotypes

# Rerun analysis without noted samples:
loadedDataFilt <- LoadAMData(finalGenotypes, targetStatus = c("Medium Quality", "High Quality")) # Load all samples with 67 or more working loci
uniqueBearsFilt <- allelematch::amUnique(loadedDataFilt$Data, multilocusMap = loadedDataFilt$AlleleKey, alleleMismatch = mmCutoff) # use stringent 10

# Save results as report as well as csv-file:
allelematch::summary.amUnique(object = uniqueBearsFilt, html = paste0("unique_bears_filt_", mmCutoff, "_v1.html"))
allelematch::summary.amUnique(object = uniqueBearsFilt, csv = paste0("unique_bears_filt_", mmCutoff, "_v1.csv"))

# Check if there are orphans still:
print(GetOrphans(hiqSamples = samples75, allClusters = lapply(uniqueBearsFilt$pairwise, function(x) {x$match$index}))) # make sure that there are no orphans

# Quick overview of statuses of samples:
table(finalGenotypes$Status)
```

# Calculate sex and generate statistics output: (remove?)
```{r}
sexGenotypes$Status <- finalGenotypes$Status[match(sexGenotypes$Sample, finalGenotypes$Sample)]
sexDetClusters <- sexGenotypes[sexGenotypes$Status %in% c("Medium Quality", "High Quality"),]
sexDetClusters$Cluster <- bearsFiltResult$uniqueIndex[match(sexDetClusters$Sample, bearsFiltResult$matchIndex)]

SexChooser <- function(clusterName, inputDF, minimumX = 1, minimumY = 3) {
  curMarkers <- inputDF[inputDF$Cluster == clusterName, ]
  curMarkers[rowSums(curMarkers[grep("^X", colnames(curMarkers))] == "") == 3, ] <- "" #rep("", ncol(curMarkers))
  presentX <- any(rowSums(curMarkers[grep("^X", colnames(curMarkers))] != "") >= minimumX)
  presentY <- any(rowSums(curMarkers[grep("^Y", colnames(curMarkers))] != "") >= minimumY)
  if(presentY) {
    SNPSex <- "Hane"
  } else if(presentX) {
    SNPSex <- "Hona"
  } else {
    SNPSex <- "Obestämd"
  }
  return(data.frame(Cluster = clusterName, SNP_sex = SNPSex))
}

bearSexList <- lapply(unique(sexDetClusters$Cluster), SexChooser, sexDetClusters, minimumX = 1, minimumY = 3) # minimum 1 X to get determined, minimum 3 Y to be a male
bearSexSummary <- do.call(rbind, bearSexList)
sexDetClusters$SNP_Sex <- bearSexSummary$SNP_sex[match(sexDetClusters$Cluster, bearSexSummary$Cluster)]
table(sexDetClusters$SNP_Sex) # summarise sex of samples
statisticsOutFile <- cbind(sexDetClusters[, -c(8)], QCGenotypes[match(sexDetClusters$Sample, QCGenotypes$Sample), -c(1, 2)]) 
writexl::write_xlsx(x = statisticsOutFile, path = "Outputs/clustered_bear_samples_id_sex_genotypes_v1.xlsx")
```

# Rovbase input functions:
```{r}
SexChooser <- function(clusterName, martinDF, minimumX = 1, minimumY = 3) {
  curMarkers <- martinDF[martinDF$Cluster == clusterName, ]
  curMarkers[rowSums(curMarkers[grep("^X", colnames(curMarkers))] == "") == 3, ] <- "" # set all columns to nothing in case no X markers are present
  presentX <- any(rowSums(curMarkers[grep("^X", colnames(curMarkers))] != "") >= minimumX)
  presentY <- any(rowSums(curMarkers[grep("^Y", colnames(curMarkers))] != "") >= minimumY)
  if(presentY) {
    SNPSex <- "Hane"
  } else if(presentX) {
    SNPSex <- "Hona"
  } else {
    SNPSex <- "Obestämd"
  }
  return(data.frame(Cluster = clusterName, SNP_sex = SNPSex))
}

DetermineID <- function(allClusters, outDF, bearSexMeta = sexedBearIDs, SSRDataBecky = SSRDatabase) {
  curClust <- allClusters[1]
  remClusters <- allClusters[-1]
  print(curClust)
  testCluster <- bearSexMeta$Sample[bearSexMeta$Cluster == curClust]
  testIds <- SSRDataBecky$individ[SSRDataBecky$index %in% testCluster] # try with one with several SSR samples
  if(length(testIds) == 1) { # if one name found
    outName <- testIds
  } else if(length(testIds > 1)) {
    if(length(unique(testIds)) == 1) { # if all names the same
      outName <- testIds[1]
    } else {
      outName <- "0_MULTIPLE_NAMES" # if cluster has multiple different SSR IDs
    }
  } else { # if the cluster had no SSR name (new or otherwise)
    outName <- "0_NO_NAME"
  }
  # Check if name is repeated, and if so handle:
  if(outName %in% outDF$ID[grepl("^BI|^NRM_", outDF$ID)]) { # if name exists already
    otherCluster <- outDF$Cluster[outDF$ID == outName]
    otherSize <- sum(bearSexMeta$Cluster %in% otherCluster, na.rm = TRUE)
    currSize <- sum(bearSexMeta$Cluster %in% curClust, na.rm = TRUE)
    if(currSize > otherSize) { # if current cluster has more samples
      outDF$ID[outDF$Cluster == otherCluster] <- "0_REPEATED_NAME" # name is kept for current and the other is changed
    } else {
      outName <- "0_REPEATED_NAME" # current cluster gets the new name since it is smaller
    }
  }
  # Check if to recurse or return final output:
  if(length(remClusters) > 0) {
    DetermineID(remClusters, rbind(outDF, data.frame(Cluster = curClust, ID = outName)), bearSexMeta = bearSexMeta)
  } else {
    return(rbind(outDF, data.frame(Cluster = curClust, ID = outName)))
  }
} # failed bears are not handled well by this, BEAR gets multiple names tag for some reason

SexChooserSample <- function(sampleName, allDataDF, minimumX = 1, minimumY = 3) {
  sampleRow <- allDataDF[allDataDF$Sample == sampleName, ]
  # sampleRow <- as.data.frame(sampleRow)
  # sampleRow[is.na(sampleRow)] <- ""
  # print(sampleRow)
  sampleRow[rowSums(sampleRow[grep("^X", colnames(sampleRow))] == "") == 3, ] <- ""  # set all columns to nothing in case no X markers are present
  presentX <- any(rowSums(sampleRow[grep("^X", colnames(sampleRow))] != "") >= minimumX)
  presentY <- any(rowSums(sampleRow[grep("^Y", colnames(sampleRow))] != "") >= minimumY)
  if(presentY) {
    SNPSex <- "Hane"
  } else if(presentX) {
    SNPSex <- "Hona"
  } else {
    SNPSex <- "Obestämd"
  }
  return(SNPSex)
}

SexChooserSample2 <- function(sampleName, allDataDF, minimumX = 2, minimumY = 3) {
  sampleRow <- allDataDF[allDataDF$Sample == sampleName, ]
  sampleRow[sum(sampleRow[grep("^X-", colnames(sampleRow))] == "") == 3] <- ""  # set all markers to nothing in case no X markers are present
  atleastNX <- any(sum(sampleRow[grep("^X-", colnames(sampleRow))] != "") >= minimumX)
  atleastNY <- any(sum(sampleRow[grep("^Y-", colnames(sampleRow))] != "") >= minimumY)
  zeroY <- any(sum(sampleRow[grep("^Y-", colnames(sampleRow))] != "") == 0)
  marketHet <- function(x) {unlist(strsplit(x, ""))[1] != unlist(strsplit(x, ""))[2]}
  zeroXHet <- sum(unlist(lapply(sampleRow[, grepl("^X-", colnames(sampleRow))], marketHet)), na.rm = TRUE) == 0
  if(atleastNY & zeroXHet) { # if min 1 X and 3 Y markers worked and 0 X are heterozygotes
    SNPSex <- "Hane"
  } else if(atleastNX & zeroY) { # if min 2 X and 0 Y markers worked
    SNPSex <- "Hona"
  } else {
    SNPSex <- "Obestämd"
  }
  # return(c(sampleName, SNPSex))
  return(SNPSex)
}

GenerateLopnummer <- function(clusterNames, allData, startNumber, lansbokstav, yearYY, outDF = data.frame(), deadStartNumber) {
  # clusterName <- as.character(clusterNames[1])
  clusterName <- clusterNames[1]
  remClusters <- clusterNames[-1]
  curSamples <- allData$Sample[allData$ID_ref == clusterName]
  if(startsWith(unique(sexedBearIDs$ID_ref[sexedBearIDs$ID_ref == clusterName]), "BI")) {
    outDF <- rbind(outDF, data.frame(ID_ref = clusterName, Lopnummer = ""))
    newNumber <- startNumber
    newDeadNumber <- deadStartNumber
  } else {
    # if(any(startsWith(curSamples, "M"))) { # if cluster contains a tissue sample
    if(length(curSamples) == 1 & any(startsWith(curSamples, "M"))) { # if lone tissue sample # edited
      # outDF <- rbind(outDF, data.frame(ID_ref = clusterName, Lopnummer = paste0("B", deadStartNumber, "+")))
      outDF <- rbind(outDF, data.frame(ID_ref = clusterName, Lopnummer = paste0("B", formatC(deadStartNumber, width = 3, format = "d", flag = "0"), "+")))
      newNumber <- startNumber
      newDeadNumber <- deadStartNumber + 1
    } else if(length(curSamples) > 1 & any(startsWith(curSamples, "M"))) { # if cluster contains a tissue sample # addition
      # outDF <- rbind(outDF, data.frame(ID_ref = clusterName, Lopnummer = paste0(lansbokstav, yearYY, "-", startNumber, "+")))
      outDF <- rbind(outDF, data.frame(ID_ref = clusterName, Lopnummer = paste0(lansbokstav, yearYY, "-", formatC(startNumber, width = 3, format = "d", flag = "0"), "+")))
      newNumber <- startNumber + 1
      newDeadNumber <- deadStartNumber
    } else {
      # outDF <- rbind(outDF, data.frame(ID_ref = clusterName, Lopnummer = paste0(lansbokstav, yearYY, "-", startNumber)))
      outDF <- rbind(outDF, data.frame(ID_ref = clusterName, Lopnummer = paste0(lansbokstav, yearYY, "-", formatC(startNumber, width = 3, format = "d", flag = "0"))))
      newNumber <- startNumber + 1
      newDeadNumber <- deadStartNumber
    }
  }
  if(length(remClusters) > 0) {
    GenerateLopnummer(clusterNames = remClusters, allData = allData, startNumber = newNumber, lansbokstav = lansbokstav, yearYY = yearYY, outDF = outDF, deadStartNumber = newDeadNumber)
  } else {
    return(outDF)
  }
}
```

# Rovbase object creation:
```{r}
# Make new object and load metadata:
exportGenotypes <- finalGenotypes
SSRDatabase <- as.data.frame(read.table("../../../../bears/bear_genotyping_2025/snp_genotyping_2025/SSR_database/newdb.csv", sep = ',', header = TRUE)) # SSR database for tissues and previously non working cluster samples
rovbaseMetaData <- as.data.frame(readxl::read_xlsx("../../rovbase_metadata.xlsx"))
zombieBears <- c() # specify zombie bear sample names

# Remove geoproblems:
# geoProblems <- as.data.frame(readxl::read_xlsx("../GeoQC.xlsx"))
# geoProblems[is.na(geoProblems)] <- ""
# exportGenotypes$Status[exportGenotypes$Sample %in% geoProblems$Sample[geoProblems$Action == "Only bear"]] <- "Manual Removal"

# Generate individual sex:
bearsFiltResult <- read.table(paste0("unique_bears_filt_", mmCutoff, "_v1.csv"), sep = ",", header = TRUE)
sexGenotypes$StatusFinal <- exportGenotypes$Status[match(sexGenotypes$Sample, exportGenotypes$Sample)]
sexedBearIDs <- sexGenotypes[sexGenotypes$StatusFinal %in% c("Medium Quality", "High Quality"),]
sexedBearIDs$Cluster <- bearsFiltResult$uniqueIndex[match(sexedBearIDs$Sample, bearsFiltResult$matchIndex)]
bearSexListRB <- lapply(unique(sexedBearIDs$Cluster), SexChooser, sexedBearIDs, minimumY = 3) # minimum 3 Y to be a male
bearSexSummaryRB <- do.call(rbind, bearSexListRB)
sexedBearIDs$SNP_Sex <- bearSexSummaryRB$SNP_sex[match(sexedBearIDs$Cluster, bearSexSummaryRB$Cluster)]

# Get SSR IDs, handle zombie bears and generate NRM-names for new individuals:
identityDF <- DetermineID(unique(sexedBearIDs$Cluster), data.frame(Cluster = c(), ID = c()))
zombieClusters <- sexedBearIDs$ClusterNum[sexedBearIDs$Sample %in% zombieBears] # get zombie clusters
identityDF$ID[identityDF$Cluster %in% zombieClusters] <- "0_REPEATED_NAME" # give zombie clusters repeated name IDs
nrmNumStart <- sort(as.numeric(gsub("NRM_", "", SSRDatabase$individ[grepl("^NRM_", SSRDatabase$individ)])), decreasing = TRUE)[1] + 1 # get nrm name start
nrmNamesNew <- paste0("NRM_", nrmNumStart:(nrmNumStart + sum(identityDF$ID == "0_REPEATED_NAME", na.rm = TRUE) - 1)) # generate new nrm names
identityDF$ID[identityDF$ID == "0_REPEATED_NAME"] <- nrmNamesNew # give nrm names to clusters with repeated names
sexedBearIDs$ID_ref <- identityDF$ID[match(sexedBearIDs$Cluster, identityDF$Cluster)] # match IDs with clusters
sexedBearIDs$ID_ref <- as.character(sexedBearIDs$ID_ref) # cast it as character since it is a weird form of character (read_xlsx?)

# Handle clusters split by SSR (by trusting SSR):
sexedBearIDs$ID_ref[sexedBearIDs$ID_ref == '0_MULTIPLE_NAMES'] <- SSRDatabase[match(sexedBearIDs$Sample[sexedBearIDs$ID_ref == '0_MULTIPLE_NAMES'], SSRDatabase$index), 8] # split multiple names cluster

# Fix 0_NO_NAMES:
exportGenotypes$Status[exportGenotypes$Sample %in% sexedBearIDs$Sample[sexedBearIDs$ID_ref == "0_NO_NAME"]] <- "No SSR Representative"
sexedBearIDs <- sexedBearIDs[!(sexedBearIDs$ID_ref == "0_NO_NAME"), ]

# Generate sample sex:
sexedBearIDs$Sample_sex <- lapply(sexedBearIDs$Sample, SexChooserSample, sexedBearIDs)

# Generate year found:
sexedBearIDs$YearFound <- unlist(lapply(rovbaseMetaData$Funnetdato[match(sexedBearIDs$Sample, rovbaseMetaData$`Strekkode (Prøve)`)], function(x) {strsplit(as.character(x), "-")[[1]][1]}))

# Figure out highest löpnummer for new individuals found dead:
rovbaseNamesLop <- unlist(lapply(strsplit(rovbaseMetaData$Individ, " "), `[`, 2))
rovbaseNamesLop[is.na(rovbaseNamesLop)] <- ""
rovbaseNamesLopDead <- max(as.numeric(gsub("B", "", rovbaseNamesLop[grepl("^B\\d+", rovbaseNamesLop)]))) + 1

# Generate sample fylke:
sexedBearIDs$Fylke <- rovbaseMetaData$Fylke[match(sexedBearIDs$Sample, rovbaseMetaData$`Strekkode (Prøve)`)]
sexedBearIDs$Fylke[is.na(sexedBearIDs$Fylke)] <- ""

# Generate löpnummer:
lopnummerDF1 <- GenerateLopnummer(clusterNames = unique(sexedBearIDs$ID_ref[sexedBearIDs$Fylke == "Västernorrlands län (S)"]), allData = sexedBearIDs, startNumber = 1, lansbokstav = "Y", yearYY = "25", deadStartNumber = rovbaseNamesLopDead) # Västernorrland

lopnummerDF2 <- GenerateLopnummer(clusterNames = unique(sexedBearIDs$ID_ref[sexedBearIDs$Fylke != "Västernorrlands län (S)"]), allData = sexedBearIDs, startNumber = 1, lansbokstav = "PROBLEM", yearYY = "25", deadStartNumber = max(as.numeric(gsub("B|\\+", "", lopnummerDF1$Lopnummer[grepl("^B\\d+\\+", lopnummerDF1$Lopnummer)]))) + 1) # everything else

lopnummerDF <- rbind(lopnummerDF1, lopnummerDF2)
sexedBearIDs$Löpnummer <- lopnummerDF$Lopnummer[match(sexedBearIDs$ID_ref, lopnummerDF$ID_ref)]

# Remove NA values
sexedBearIDs[is.na(sexedBearIDs)] <- ""
```

# Generate Rovbase input files:
```{r}
### Working samples (tissues and scats):
## Generate rovbaseIndividDF:
rovbaseIndividDF <- sexedBearIDs[!duplicated(sexedBearIDs$ID_ref) & grepl("NRM_", sexedBearIDs$ID_ref), ]
rovbaseIndividDF <- cbind(ArtsID = "3", Individnavn = rovbaseIndividDF$Löpnummer, KjønnID = rovbaseIndividDF$SNP_Sex, Dødsår = rovbaseIndividDF$YearFound, Merknad = "")
rovbaseIndividDF <- as.data.frame(rovbaseIndividDF)

## Generate rovbaseInputWorking:
rovbaseInputWork <- cbind(DNAID = "", Strekkode = sexedBearIDs$Sample, RovbaseID = "", ArtsID = "3", PrøvestatusID = "1", KjønnID = ifelse(sexedBearIDs$Sample_sex == "Hane", "1", ifelse(sexedBearIDs$Sample_sex == "Hona", "2", "3")), MetodeID = "32", AnalysertAvID = "10", Merknad = "", IndividID = gsub("NRM_.+", "", sexedBearIDs$ID_ref), IndividNavn = sexedBearIDs$Löpnummer, ReferanseID = "", Referansetekst = "")
rovbaseInputWork <- as.data.frame(rovbaseInputWork)

### Bear-only samples (non-working but identified as bear):
{rovbaseInputBear <- exportGenotypes[!(exportGenotypes$Status %in% c("Control", "Fail Quality", "Medium Quality", "High Quality", "Exclude")), ] # remove all control, fully failed or working samples
rovbaseInputBear <- cbind(DNAID = "", Strekkode = rovbaseInputBear[, "Sample"], RovbaseID = "", ArtsID = "3", PrøvestatusID = "1", KjønnID = "3", MetodeID = "32", AnalysertAvID = "10", Merknad = "", IndividID = "", IndividNavn = "", ReferanseID = "", Referansetekst = "")}
rovbaseInputBear <- as.data.frame(rovbaseInputBear)

### Failed samples:
{rovbaseInputFail <- exportGenotypes[exportGenotypes$Status == "Fail Quality", ] # extract failed samples
rovbaseInputFail <- cbind(DNAID = "", Strekkode = rovbaseInputFail[, "Sample"], RovbaseID = "", ArtsID = "14", PrøvestatusID = "2", KjønnID = "3", MetodeID = "32", AnalysertAvID = "10", Merknad = "", IndividID = "", IndividNavn = "", ReferanseID = "", Referansetekst = "")}
rovbaseInputFail <- as.data.frame(rovbaseInputFail)
```

# QC before final delivery:
```{r}
# RovbaseIndividDF:
length(rovbaseIndividDF$Individnavn) == length(unique(rovbaseIndividDF$Individnavn)) # is every Individnavn unique?
length(rovbaseIndividDF$Individnavn) 
length(unique(rovbaseIndividDF$Individnavn))

# All names written to outputs:
allOutputNames <- c(rovbaseInputWork$Strekkode, rovbaseInputBear$Strekkode, rovbaseInputFail$Strekkode)

length(exportGenotypes$Sample) # number of samples in
length(allOutputNames) # number of samples out
length(unique(allOutputNames)) # number of unique samples out
View(exportGenotypes[!(exportGenotypes$Sample %in% allOutputNames),]) # did we lose any samples that should be kept?

table(exportGenotypes$Status[(exportGenotypes$Sample %in% rovbaseInputWork$Strekkode)]) # statuses of working samples
table(exportGenotypes$Status[(exportGenotypes$Sample %in% rovbaseInputBear$Strekkode)]) # statuses of only-bear samples
table(exportGenotypes$Status[(exportGenotypes$Sample %in% rovbaseInputFail$Strekkode)]) # statuses of failed samples
```

# Write output:
```{r}
writexl::write_xlsx(rbind(rovbaseInputWork, rovbaseInputBear, rovbaseInputFail), "Outputs/Analysresultat_björn_20XX_rovbase_prover_v1_raw.xlsx")
writexl::write_xlsx(rovbaseIndividDF, "Outputs/Analysresultat_björn_20XX_rovbase_nya_individ_v1_raw.xlsx")
```